Exploring Hillary Clinton's Emails\thanks{STATS 601 final project. All of the code used to download, process, and analyze the data for this project is available at \url{https://github.com/lbybee/601_Final_Project} and has been open-sourced under the MIT license.}

### 2016-04-20 paper/paper.tex
Minor changes.

The primary parameter that we need to specify for LDA is the number of topics. Since our ultimate goal is to find sensible topics that can be used to understand the email corpus, we initially turned to coherence measures, which attempt to quantify whether estimated topics would make sense to a human observer. In particular, we considered the UMass and UCI measures.\footnote{add bib here} However, the coherence of our topics did not appear to vary much across a wide range of reasonable topic numbers, from roughly 15 to 50 topics used. As a result we manually examined the results from models using a range of topics and attempted to select the most parsimonious model, resulting in a 30 topic model.

@@

Given that we have time stamps foe each email, we can also examine how these topics are used over time. Figure~\ref{fig:topic_time_plots} plots the mean monthly topic proportion for each of the topics in Table~\ref{tab:content_topics}.

\begin{figure}[htb]
\centering
\begin{subfigure}[Israel]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot6.pdf}
    \caption{Israel} \label{fig:t1}
\end{subfigure}
\begin{subfigure}[Election]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot11.pdf}
    \caption{Election} \label{fig:t2}
\end{subfigure}
\begin{subfigure}[Libya]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot18.pdf}
    \caption{Libya} \label{fig:t3}
\end{subfigure}
\begin{subfigure}[Afghanistan]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot27.pdf}
    \caption{Afghanistan} \label{fig:t4}
\end{subfigure}
\begin{subfigure}[Int. Dev.]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot23.pdf}
    \caption{Int. Dev.} \label{fig:t5}
\end{subfigure}
\begin{subfigure}[Obama]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot25.pdf}
    \caption{Obama} \label{fig:t6}
\end{subfigure}
\caption{Average monthly topic proportions.}
\label{fig:topic_time_plots}
\end{figure}

We can see that our topics seem to be correlated with the expected real-world events. The Israel topic's first peak corresponds to the July 26th, 2010 joint Israeli and Romanian helicopter disaster, while the second peak corresponds to the September 9th, 2011 attack on the Israel embassy in Egypt. Similarly, for the election topic each of the peaks corresponds to a U.S. election. Looking at the Libya topic, the first peak corresponds to the fall of Gaddafi's adminstration in October of 2011, while the second peak corresponds to the Benghazi attack on September 11th, 2012. These kinds of patterns over time are interesting to verify, and could also be used to identify the prevalent topics of discussion for times when there are not obvious world events driving discussion.\footnote{These monthly topic proportion plots for all our estimate topics are available at \url{https://github.com/lbybee/601_Final_Project/tree/master/images}.}

@@

\begin{table}[htb] \centering
\begin{tabular}{ccc}
  \toprule
  Source & Success Rate & Testing Observations \\
  \midrule
  Hillary Clinton & 0.74 & 849 \\
  Philippe Reines & 0.06 & 34 \\
  Claire Coleman & 0.52 & 27 \\
  Lauren Jiloty & 0.42 & 71 \\
  Huma Abedin & 0.36 & 376 \\
  Jake Sullivan & 0.23 & 410 \\
  Sidney Blumenthal & 0.29 & 87 \\
  Cherly Mills & 0.31 & 491 \\
  Anne-Marie Slaughter & 0.36 & 42 \\
  Monica Hanley & 0.09 & 53 \\
  Judith McHale & 0.25 & 28 \\
  Robert Russo & 0.00 & 10 \\
  Richard Verma & 0.26 & 19 \\
  Wendy Sherman & 0.08 & 12 \\
  Melanne Verveer & 0.30 & 30 \\
  Lona Valmoro & 0.34 & 41 \\
  \bottomrule
\end{tabular}
\caption{Multinomial logistic regression successes}
\label{tab:mlr_success}
\end{table}

@@

The results we see here all us to tell a story about the email senders that corresponds to our intution based on each of the sender's backgrounds.  Sidney Blumenthal is strongly associated with the Middle East, foreign policy and general politics topics.  He doesn't have much to say about Hillary or her significance to the press and generally doesn't talk muhc about meetings.  Huma Abedin and Jake Sullivan provide advice on the Middle east and foreign policy.  Judith McHale focuses her emails on foreign policy and handling press issues.  While all this is going on Hillary spends most of her time discussing meetings.

>>>>

The primary parameter that we need to specify for LDA is the number of topics. Since our ultimate goal is to find sensible topics that can be used to understand the email corpus, we initially turned to coherence measures, which attempt to quantify whether estimated topics would make sense to a human observer. In particular, we considered the UMass and UCI measures.\footnote{add bib here} However, the coherence of our topics did not appear to vary much across a wide range of reasonable topic numbers, anywhere from 15 to 50 topics used. As a result we manually examined the results from models using a range of topics and attempted to select the most parsimonious model, resulting in a 30 topic model.

@@

Given that we have time stamps foe each email, we can also examine how prevalent each topic is over time. Figure~\ref{fig:topic_time_plots} shows the mean monthly topic proportion for each of the topics in Table~\ref{tab:content_topics}.

\begin{figure}[htb]
\centering
\begin{subfigure}[Israel]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot6.pdf}
    \caption{Israel} \label{fig:t1}
\end{subfigure}
\begin{subfigure}[Elections]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot11.pdf}
    \caption{Elections} \label{fig:t2}
\end{subfigure}
\begin{subfigure}[Libya]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot18.pdf}
    \caption{Libya} \label{fig:t3}
\end{subfigure}
\begin{subfigure}[Afghanistan]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot27.pdf}
    \caption{Afghanistan} \label{fig:t4}
\end{subfigure}
\begin{subfigure}[Int. Dev.]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot23.pdf}
    \caption{Int. Dev.} \label{fig:t5}
\end{subfigure}
\begin{subfigure}[Obama]{.30\linewidth}
    \includegraphics[width=\linewidth]{../images/time_plot25.pdf}
    \caption{Obama} \label{fig:t6}
\end{subfigure}
\caption{Average monthly topic proportions.}
\label{fig:topic_time_plots}
\end{figure}

We can see that our topics seem to be correlated with the expected real-world events. The Israel topic's first peak corresponds to the July 26th, 2010 joint Israeli and Romanian helicopter disaster, while the second peak corresponds to the September 9th, 2011 attack on the Israel embassy in Egypt. Similarly, for the election topic each of the peaks corresponds to a U.S. election. Looking at the Libya topic, the first peak corresponds to the fall of Gaddafi's adminstration in October of 2011, while the second peak corresponds to the Benghazi attack on September 11th, 2012. These kinds of patterns over time are interesting to verify, and could also be used to identify the prevalent topics of discussion for times when there are not obvious world events driving discussion.\footnote{These monthly topic proportion plots for all our estimated topics are available at \url{https://github.com/lbybee/601_Final_Project/tree/master/images}.}

@@

\begin{table}[htb] \centering
\begin{tabular}{ccc}
  \toprule
  Source               & Success Rate & Testing Observations \\
  \midrule
  Hillary Clinton      & 0.74         & 849 \\
  Philippe Reines      & 0.06         & 34 \\
  Claire Coleman       & 0.52         & 27 \\
  Lauren Jiloty        & 0.42         & 71 \\
  Huma Abedin          & 0.36         & 376 \\
  Jake Sullivan        & 0.23         & 410 \\
  Sidney Blumenthal    & 0.29         & 87 \\
  Cherly Mills         & 0.31         & 491 \\
  Anne-Marie Slaughter & 0.36         & 42 \\
  Monica Hanley        & 0.09         & 53 \\
  Judith McHale        & 0.25         & 28 \\
  Robert Russo         & 0.00         & 10 \\
  Richard Verma        & 0.26         & 19 \\
  Wendy Sherman        & 0.08         & 12 \\
  Melanne Verveer      & 0.30         & 30 \\
  Lona Valmoro         & 0.34         & 41 \\
  \bottomrule
\end{tabular}
\caption{Multinomial logistic regression test results.}
\label{tab:mlr_success}
\end{table}

@@

The results we see here all us to tell a story about the email senders that corresponds to our intution based on each of the sender's backgrounds. Sidney Blumenthal is strongly associated with the Middle East, foreign policy and general politics topics. He doesn't have much to say about Hillary or her significance to the press and generally doesn't talk muhc about meetings. Huma Abedin and Jake Sullivan provide advice on the Middle East and foreign policy. Judith McHale focuses her emails on foreign policy and handling press issues. While all this is going on Hillary spends most of her time discussing meetings.
